---
title: "Introduction of a Binomial random variable"
author: "Jiangying Zhong"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial random variable}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```
## Binomial

The package `"binomial"` is a minimal implementation for calculating probabilities of a Binomial random variable.

## check the private attribution 
The first step is to check the private attributions of a binomial random varible.
```{r}
check_trials(trials=5)
check_prob(prob=0.5)
check_success(succcess=2,trials=5)
```
In general, the trials must be a positive number,the prob must be a positive number between 0 and 1, and the success must be a positive number less than the trials. Addition to this, the prob must be 1 length.

## auxiliary functions for summary measures
Then, you can use the auxiliary functions to simulate the basic attributes of the binomial random variable.
```{r}
aux_mean(trials=10,prob=0.3)
aux_variable(trials=10,prob=0.3)
aux_mode(trials=10,prob=0.3)
aux_skewness(trials=10,prob=0.3)
aux_kurtosis(trials=10,prob=0.3)
```
When X is a random variable that has a binomial distribution with n trials and probability of success p, we write X ∼ Bin(n, p).
The expected value or mean of a binomial distribution is: np.
The variance is given by: np(1 − p).
For 0 < p < 1, the most likely number of success in n independent trials with probability p of success on each trial is m, the greater integer less than or equal to np + p: m = int(np + p).
The skewness of a binomial random variable can be calculated as: skewness =(1 − 2p)/sqrt(np(1 − p)).
For a binomial random variable, its kurtosis can be obtained as: kurtosis = (1 − 6p(1 − p))/np(1 − p).

## main functions to print and graph the attributions of the binomial random variable
```{r}
bin_choose(trials=5,success=2)
bin_probability(success=2,trials=5,prob=0.5)
bin_distribution(trials = 5, prob = 0.5)
plot_bindis(bin_distribution(trials = 5, prob = 0.5))
bin_cumulative(trials = 5, prob = 0.5)
plot_bincum(bin_cumulative(trials = 5, prob = 0.5))
bin_variable(trials = 10, prob = 0.3)
summary.binvar(bin_variable(trials = 10, prob = 0.3))
print.summary.binvar(summary.binvar(bin_variable(trials = 10, prob = 0.3)))
```
Use the main functions to create three objects in three classes: "bindis","bincum","binvar". Then we print different dataframes to display the contents of the objects and use plot function to display the barplots and lineplots.





